%-----------PUBLICATIONS-----------%
\section{PUBLICATIONS}
    \resumeSubHeadingListStart
    
    \vspace{10pt}        
    
        \resumePublicationheading
        {Journal Articles}{}
        
        \begin{itemize}[leftmargin=0.45in, label={}]

            \item [{[J4]}] Moon, G., \textbf{Ko, Y.}, Yi, M., \& Jun, E. (2026). Operational feasibility analysis of a cryogenic active intake device for atmosphere-breathing electric propulsion. \textit{Aerospace Science and Technology}, 112138.

            \item [{[J3]}] \textbf{Ko, Y.}, \& Jun, E. (2026). Radiative equilibrium boundary condition and correlation analysis on catalytic surfaces in DSMC. \textit{International Journal of Heat and Mass Transfer}, \textit{255}, 127693.

            \item [{[J2]}] \textbf{Ko, Y.}, \& Jun, E. (2024). Mechanism-specific chemical energy accommodation with finite-rate surface chemistry in non-equilibrium flow. \textit{Physics of Fluids}, \textit{36}(9), 096115.

            \item [{[J1]}] \textbf{Ko, Y.}, Kim, S., Moon, G., Yi, M., Park, K., Kim, Y., \& Jun, E. (2023). Parametric study on the flight envelope of a radio-frequency ion thruster based atmosphere-breathing electric propulsion system. \textit{Acta Astronautica}, \textit{212}, 198--212.
        \end{itemize}

        
        \resumePublicationheading
        {Conference Presentations}{}
        \vspace{2pt}
        \begin{itemize}[leftmargin=0.45in, label={}]
            \item [{[C13]}] \textbf{Ko, Y.}, Moon, G., \& Jun, E. (2025, Jun). \textit{Effect of surface recombination reaction on performance of intake device}. The Korean Society for Aeronautical \& Space Sciences (KSAS) Conference, Yeosu, Korea.
            \item [{[C12]}] Park, W., \textbf{Ko, Y.}, \& Jun, E. (2025, Apr). \textit{Advanced gas-surface interaction model considering atomic oxygen in very low Earth orbit}. Korean Society for Computational Fluids Engineering (KSCFE) Conference, Iksan, Korea.
            \item [{[C11]}] Ma, S., \textbf{Ko, Y.}, \& Jun, E. (2025, Apr). \textit{Validation of air-carbon ablation model of carbon-based ablation TPS using DSMC}. The Korean Society for Aeronautical \& Space Sciences (KSAS) Conference, Jeju, Korea.
            \item [{[C10]}] \textbf{Ko, Y.}, \& Jun, E. (2025, Apr). \textit{Re-entry flow analysis considering surface reaction and radiation equilibrium}. The Korean Society for Aeronautical \& Space Sciences (KSAS) Conference, Jeju, Korea.
            \item [{[C9]}] Moon, G., \textbf{Ko, Y.}, \& Jun, E. (2024, Nov). \textit{Numerical analysis of the operational concept of a cryogenic active intake device for atmosphere-breathing electric propulsion}. The Korean Society of Propulsion Engineers (KSPE) Conference, Busan, Korea.
            \item [{[C8]}] \textbf{Ko, Y.}, \& Jun, E. (2024, Jul). \textit{Reaction mechanism-specific chemical energy accommodation in Direct Simulation Monte Carlo}. 33rd International Symposium on Rarefied Gas Dynamics (RGD33), Göttingen, Germany.
            \item [{[C7]}] Moon, G., \textbf{Ko, Y.}, \& Jun, E. (2024, Jul). \textit{Feasibility analysis of a cryogenic active intake device for atmosphere-breathing electric propulsion}. 33rd International Symposium on Rarefied Gas Dynamics (RGD33), Göttingen, Germany.
            \item [{[C6]}] \textbf{Ko, Y.}, \& Jun, E. (2024, Jun). \textit{Surface reaction chemical energy accommodation model for re-entry flows}. The Korean Society for Aeronautical \& Space Sciences (KSAS) Conference, Changwon, Korea.
            \item [{[C5]}] \textbf{Ko, Y.}, \& Jun, E. (2024, Apr). \textit{Surface catalytic effect on chemical heat flux using Direct Simulation Monte Carlo}. The 3rd International Conference on High-Speed Vehicle Science and Technology (HiSST), Busan, Korea.
            \item [{[C4]}] Moon, G., \textbf{Ko, Y.}, Kim, S., Yi, M., Kim, Y., \& Jun, E. (2023, Jun). \textit{Conceptual system analysis of atmosphere-breathing electric propulsion for very-low-Earth-orbit operation}. The Korean Society for Aeronautical \& Space Sciences (KSAS) Conference, Yeosu, Korea.
            \item [{[C3]}] Jun, E., Moon, G., \textbf{Ko, Y.}, \& Kim, S. (2023, Mar). \textit{Conceptual system analysis of very-low-Earth-orbit satellites with atmosphere-breathing electric propulsion}. The 11th Asian Joint Conference on Propulsion and Power (AJCPP), Kanazawa, Japan.
            \item [{[C2]}] \textbf{Ko, Y.}, Kim, S., Moon, G., \& Jun, E. (2023, Mar). \textit{Flight envelope determination of atmosphere-breathing electric propulsion system}. The Korean Society of Propulsion Engineers (KSPE) Conference, Jeju, Korea.
            \item [{[C1]}] \textbf{Ko, Y.}, Kim, S., Moon, G., \& Jun, E. (2022, Nov). \textit{Drag compensation feasibility of an atmosphere-breathing electric propulsion system}. The Korean Society of Propulsion Engineers (KSPE) Conference, Busan, Korea.
        \end{itemize}
        
    \resumeSubHeadingListEnd